A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-15 manuscript.Rmd
Add citations.

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts and presentations---and even your CV.
To create a Markdown document, click on:

@@

Currently, there are various templates available that guide researchers in developing data analysis plans for preregistration. 
Still, with any natural-language representation of an analysis plan, there remains ambiguity when turning the natural language description of a given data analysis into code.
Here, we discuss preregistration as code (PAC) with the R package repro, which leaves no room for ambiguity.
PAC essentially reverses the process of empirical research.
Before researchers gather data, they write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results---initially based on simulated data.
Then, the source code of this manuscript serves as an unambiguous description of the analysis plan and is published as a preregistration.

@@

@@

As default, `repro` uses Docker, which is the defacto standard for cloud computing, as a container solution.
However, Docker requires administrator rights for execution.
Whereas this is no issue on most modern cloud computing infrastructures, it is often an issue in classic HPC environments.
Singularity is an alternative solution.
It was designed to run without administratot rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Importantly, this choice does not affect how code is executed inside the container.
Like with Docker, the default `Makefile` generated by `repro` comes with a mechanism to automatically send all commands to Singularity.
To reproduce an analysis with Singularity, simple add the parameter `SINGULARITY=TRUE` as follows:

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.
Sometimes it is just the required storage capacity that exceeds what Git can handle (Git gets slow around more than 100mb).
In such case we strongly recommend using [DataLad [@DataladDatalad2021]](http://handbook.datalad.org/en/latest/)[^datalad] or the below procedure to guarantee that the data has not changed.
In practice, however, there are various reasons, which may prohibit you from making your data publicly available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

>>>>

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts and presentations---and even your CV [@vitae].
To create a Markdown document, click on:

@@

Currently, there are various templates available that guide researchers in developing data analysis plans for preregistration [@osfstandard; @socpsytemp; @howtoreplicate]. 
Still, with any natural-language representation of an analysis plan, there remains ambiguity when turning the natural language description of a given data analysis into code.
Here, we discuss preregistration as code (PAC) with the R package repro, which leaves no room for ambiguity.
PAC essentially reverses the process of empirical research.
Before researchers gather data, they write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results---initially based on simulated data.
Then, the source code of this manuscript serves as an unambiguous description of the analysis plan and is published as a preregistration.

@@

[@codebook]

@@

As default, `repro` uses Docker, which is the defacto standard for cloud computing, as a container solution.
However, Docker requires administrator rights for execution.
Whereas this is no issue on most modern cloud computing infrastructures, it is often an issue in classic HPC environments.
Singularity is an alternative solution [@singularity].
It was designed to run without administratot rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Importantly, this choice does not affect how code is executed inside the container.
Like with Docker, the default `Makefile` generated by `repro` comes with a mechanism to automatically send all commands to Singularity.
To reproduce an analysis with Singularity, simple add the parameter `SINGULARITY=TRUE` as follows:

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data [@akhlaghi2020towards].
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.
Sometimes it is just the required storage capacity that exceeds what Git can handle (Git gets slow around more than 100mb).
In such case we strongly recommend using [DataLad [@DataladDatalad2021]](http://handbook.datalad.org/en/latest/)[^datalad] or the below procedure to guarantee that the data has not changed.
In practice, however, there are various reasons, which may prohibit you from making your data publicly available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.
